Using CGM to Predict CFRD in the Envision Cohort

### 2025-06-25 Christine Chan/EnVision CF/cfrd_roc.qmd
EnVision ROCs limited to first visit

```{r data cleaning}
# Import cleaned dataset
load("./Data_Clean/envision_analysis_dataset.RData")
df <- final_df
# Limit to those with CGM data (based on mean glucose) and OGTT diagnosis
df <- df %>% filter(!is.na(mean_sensor))
# Convert CV units to match Scully et al.
df$cv <- df$cv * 100
```

- **All tables and analyses below treat CGM wears as independent**, but we will need to think about how to handle this in future analyses.

@@

```{r}
df <- df %>% filter(!is.na(Diagnosis))
```

@@

```{r}
r <- roc(CFRD ~ mean_sensor, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ percent_time_over_140, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ percent_time_over_180, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ gmi, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ standard_deviation, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ cv, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ a1c_result, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

>>>>

```{r data cleaning}
set.seed(1017)
# Import cleaned dataset
load("./Data_Clean/envision_analysis_dataset.RData")
df <- final_df
# Limit to those with CGM data (based on mean glucose) and OGTT diagnosis
df <- df %>% filter(!is.na(mean_sensor),!is.na(Diagnosis))
# Convert CV units to match Scully et al.
df$cv <- df$cv * 100
# First CGM and OGTT pair only
df <- df %>%
  group_by(study_id) %>%
  slice_min(Date)
```

@@

@@

```{r}
r <- roc(CFRD ~ mean_sensor, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
gt(data.frame(ci.coords(r, "best",
  best.policy = "random",
  ret = c(c("sensitivity", "specificity", "fp", "tp", "fn", "tn"))
))) %>% fmt_number(decimals = 3)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ percent_time_over_140, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
gt(data.frame(ci.coords(r, "best",
  best.policy = "random",
  ret = c(c("sensitivity", "specificity", "fp", "tp", "fn", "tn"))
))) %>% fmt_number(decimals = 3)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ percent_time_over_180, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
gt(data.frame(ci.coords(r, "best",
  best.policy = "random",
  ret = c(c("sensitivity", "specificity", "fp", "tp", "fn", "tn"))
))) %>% fmt_number(decimals = 3)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ gmi, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
gt(data.frame(ci.coords(r, "best",
  best.policy = "random",
  ret = c(c("sensitivity", "specificity", "fp", "tp", "fn", "tn"))
))) %>% fmt_number(decimals = 3)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ standard_deviation, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
gt(data.frame(ci.coords(r, "best",
  best.policy = "random",
  ret = c(c("sensitivity", "specificity", "fp", "tp", "fn", "tn"))
))) %>% fmt_number(decimals = 3)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ cv, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
gt(data.frame(ci.coords(r, "best",
  best.policy = "random",
  ret = c(c("sensitivity", "specificity", "fp", "tp", "fn", "tn"))
))) %>% fmt_number(decimals = 3)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```

@@

```{r}
r <- roc(CFRD ~ a1c_result, data = df, quiet = T)
plot(r, print.auc = T, print.thres = T, legacy.axes = T)
ci.auc(r)
gt(data.frame(ci.coords(r, "best",
  best.policy = "random",
  ret = c(c("sensitivity", "specificity", "fp", "tp", "fn", "tn"))
))) %>% fmt_number(decimals = 3)
gt(coords(r, "all", ret = "all")) %>% fmt_number(decimals = 3)
```
